Nonparametric Goodness-of-Fit Tests for Discrete Null Distributions

### 2010-11-10 rjournal/RJtemplate.tex
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/ks-test@26 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\abstract{
A general theory for extending nonparametric goodness-of-fit tests
to discrete null distributions has existed
for several decades. Despite this, modern statistical software
has generally failed to provide this methodology
to users. We offer a revision of R's \code{ks.test()} function
and a new \code{cvm.test()} function that serve to fill this need
in the R language for two of the most popular nonparametric
goodness-of-fit tests. This paper describes these contributions and
provides examples of their usage. Particular attention is given
to various numerical issues that arise in their implementation.
}

@@

In their most basic form, the nonparametric goodness-of-fit
tests are intended for continuous null distributions, but they have
also been adapted for use with discrete null distributions.  Unfortunately,
most modern statistical software has failed to incorporate these discrete
versions, leaving researchers with the $\chi^2$ test or in the unfortunate
position of applying a nonparametric test designed for continuous null
distributions and hoping for the best.
As we will see, the latter choice can be particularly dangerous
in the small sample setting. This paper presents a revision of R's
\code{ks.test()} function and a new \code{cvm.test()} function to
fill this void for researchers and practitioners in the R environment.

@@

data:  x 
D^+ = 0.04, p-value = 0.9231
alternative hypothesis:
the CDF of x lies above the null hypothesis 
\end{Soutput}
\end{Schunk}

JAY: reconsider simulation.  Not really needed, if we have citations for
the conservatism points, etc...?  The code for this is in the JSS folder.
if we want to revisit it.

Finally, we employ two of the Cram\'{e}r-von Mises tests.  Taylor, are these
your ``cynical example'' that you commented on, or did you have something
in addition to these?  What should be discussed here?

\begin{Schunk}
\begin{Sinput}
> library(cvm.test)
> cvm.test(x, ecdf(1:10))
\end{Sinput}
\begin{Soutput}
	Cramer-von Mises - W2

>>>>

\abstract{
Methodology extending nonparametric goodness-of-fit tests
to discrete null distributions has existed
for several decades. Despite this, modern statistical software
has generally failed to provide this methodology
to users. We offer a revision of R's \code{ks.test()} function
and a new \code{cvm.test()} function that serve to fill this need
in the R language for two of the most popular nonparametric
goodness-of-fit tests. This paper describes these contributions and
provides examples of their usage. Particular attention is given
to various numerical issues that arise in their implementation.
}

@@

*** Citations in the paragraph above?  Also check the body of paper. ***

In their most basic forms, the nonparametric goodness-of-fit
tests are intended for continuous null distributions, but they have
also been adapted for use with discrete null distributions.  Unfortunately,
most modern statistical software have failed to incorporate these discrete
versions, leaving researchers with the $\chi^2$ test or in the unfortunate
position of applying a nonparametric test designed for continuous null
distributions and hoping for the best.
As we will see, the latter choice can be particularly dangerous
with small sample sizes. This paper presents a revision of R's
\code{ks.test()} function and a new \code{cvm.test()} function to
fill this void for researchers and practitioners in the R environment.

@@

data:  x 
D^+ = 0.04, p-value = 0.9231
alternative hypothesis:
the CDF of x lies above the null hypothesis 
\end{Soutput}
\end{Schunk}
A different toy example shows the dangers of using R's existing
\code{ks.test()} function:
\begin{Schunk}
\begin{Sinput}
> ks.test(rep(1, 3), ecdf(1:3))
\end{Sinput}
\begin{Soutput}
	One-sample Kolmogorov-Smirnov test

data:  rep(1, 3) 
D = 0.6667, p-value = 0.04938
alternative hypothesis: two-sided 
\end{Soutput}
\end{Schunk}
If, instead, either \code{exact=FALSE} is used with the new
\code{ks.test()} function, or if the original \code{stats::ks.test()}
is used, the reported p-value is 0.1389.

Finally, we employ two of the Cram\'{e}r-von Mises tests.  Need short discussion,
and we could use a good cyclical example:
\begin{Schunk}
\begin{Sinput}
> library(cvm.test)
> cvm.test(x, ecdf(1:10))
\end{Sinput}
\begin{Soutput}
	Cramer-von Mises - W2
